### 2022-03-23 paper/localpsf.tex
minor changes

>>>>

\begin{tabular}{lll}
	Variable name & Approximate size & Variable \\
	\hline
	$N$ & $10^3$--$10^9$ & Number of finite element degrees of freedom \\
	$b$ & $5$--$25$ & number of impulse response batches \\
	$r$ & $10$--$30$ & H-matrix rank \\
	$k$ & $5$--$15$ & number of nearest neighbors \\
	$\{\eta_b\}_{b=1}^\text{num\_batches}$ & $\text{num\_batches}$ actions of $\mathcal{A}$
\end{tabular}

$k_\text{hmatrix}$, $k_\text{nbrs}$, $k_\text{batches}$

\begin{tabular}{ll}
	$V$ & $1$ action of $\mathcal{A}^T$ \\
	$\mu$ & $d$ actions of $\mathcal{A}^T$ \\
	$\Sigma$ & $d(d+1)/2$ actions of $\mathcal{A}^T$ \\
	$\{\eta_b\}_{b=1}^\text{num\_batches}$ & $\text{num\_batches}$ actions of $\mathcal{A}$
\end{tabular}
